How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-24 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Use minutes for all time measurements

k2 <- list(s1k2, s2k2, s3k2, s4k2, s5k2)
k2_lognormconsts <- sapply(k2, function(x) x$quad$normalized_posterior$lognormconst)
k2_times <- sapply(k2, function(x) x$time)

@@

k3 <- list(s1k3, s2k3, s3k3, s4k3, s5k3, s7k3, s8k3)
k3_lognormconsts <- sapply(k3, function(x) x$quad$normalized_posterior$lognormconst)
k3_times <- sapply(k3, function(x) x$time)

@@

k5 <- list(s1k5, s2k5, s3k5, s4k5, s5k5)
k5_lognormconsts <- sapply(k5, function(x) x$quad$normalized_posterior$lognormconst)
k5_times <- sapply(k5, function(x) x$time)

>>>>

k2 <- list(s1k2, s2k2, s3k2, s4k2, s5k2)
k2_lognormconsts <- sapply(k2, function(x) x$quad$normalized_posterior$lognormconst)
k2_times <- sapply(k2, function(x) as.numeric(x$time, units = "mins"))

@@

k3 <- list(s1k3, s2k3, s3k3, s4k3, s5k3, s7k3, s8k3)
k3_lognormconsts <- sapply(k3, function(x) x$quad$normalized_posterior$lognormconst)
k3_times <- sapply(k3, function(x) as.numeric(x$time, units = "mins"))

@@

k5 <- list(s1k5, s2k5, s3k5, s4k5, s5k5)
k5_lognormconsts <- sapply(k5, function(x) x$quad$normalized_posterior$lognormconst)
k5_times <- sapply(k5, function(x) as.numeric(x$time, units = "mins"))
